### 2016-03-22 pde_two/elliptic.tex
updated many things

We will begin the discussion of Elliptic functions by analyzing the familiar trig functions, $\sin$ and
$\cos$. Consider the following system of ODEs:
\[
\begin{cases}
\frac{\dx}{\dt} = y\\
\frac{\dy}{\dt} = -x
\end{cases}
\]
This system has the solution $x(t)=\cos{t}$ and $y(t)=\sin{t}$. We will use this definition to formulate
the Elliptic functions.\\

We define a system of ODE's by letting $k\in(0,1)$ and $t\in\RR$ representative of time. We can define
three functions, $sn(t,k),cn(t,k),dn(t,k)$, as solutions to the system
\[
\begin{cases}
\frac{\dx}{\dt} = yz\\
\frac{\dy}{\dt} = -zx\\
{\dz\over\dt}=-k^{2}xy
\end{cases}
\implies
\begin{cases}
{d\over\dt}sn(t,k)=cn(t,k)dn(t,k)\\
{d\over\dt}cn(t,k)=-dn(t,k)sn(t,k)\\
{d\over\dt}dn(t,k)=-k^{2}sn(t,k)cn(t,k)
\end{cases}
\]
The functions are not arbitrary; they have special properties. The first one we notice is that
\[
\lim_{k\to0^{+}}sn(t,k)=\sin{t}
\qquad\lim_{k\to0^{+}}cn(t,k)=\cos{t}
\qquad\lim_{k\to0^{+}}dn(t,k)=1.
\]
In addition, we have that
\[
\lim_{k\to1^{-}}sn(t,k)=\tanh{t}
\qquad\lim_{k\to1^{-}}cn(t,k)=\sech{t}
\qquad\lim_{k\to1^{-}}dn(t,k)=\sech{t}.
\]

>>>>

\section{Introduction}

The Jacobi Elliptic functions come from the result of integrating certain algebraic functions. The
functions arose due to the lack on any elementary antiderivative to
\[
u=\int_{0}^{\phi}{d\theta\over\sqrt{1-k^{2}\sin^{2}{\theta}}}.
\]
The Jacobi Elliptic functions provide a way to express the solution to this integral via the properties
\begin{align*}
sn(u)&=sn\left(\int_{0}^{\phi}{d\theta\over\sqrt{1-k^{2}\sin^{2}{\theta}}}\right)=\sin{\phi}\\
cn(u)&=cn\left(\int_{0}^{\phi}{d\theta\over\sqrt{1-k^{2}\sin^{2}{\theta}}}\right)=\cos{\phi}\\
dn(u)&=dn\left(\int_{0}^{\phi}{d\theta\over\sqrt{1-k^{2}\sin^{2}{\theta}}}\right)=
\sqrt{1-k^{2}\sin^{2}{\phi}}.
\end{align*}

The elliptic functions end up being applicable to more than just finding the antiderivative of $u$.
We can express the solutions to several differential equations in terms of these functions, much like
we can with $\sin{}$ and $\cos{}$. For example, the system
\[
\begin{cases}
\dot{x} = yz\\
\dot{y} = -zx\\
\dot{z} = -k^{2}xy
\end{cases}
\qquad
\text{where}
\qquad
\begin{cases}
x(0)=0\\
y(0)=1\\
z(0)=1
\end{cases}
\]
can be solved by these elliptic functions, when subject to the initial conditions. More interestingly,
we can find the solutions for several ODEs via the elliptic functions.

\subsection{Applications to ODEs}
Consider the second order ODE
\[
\begin{cases}
\ddot{x} = (1-x^{2})(1-k^{2}x^{2})\\
\dot{x}(0)=1\\
x(0)=0
\end{cases}.
\]
Recall that we defined the Jacobi Elliptic functions as solutions to a prior system of ODEs. We had
the relationship that $\dot{x}=yz$, where $y$ and $z$ were functions of $t$. Taking another derivative
yields $\ddot{x}=\dot{y}z+y\dot{z}$. We additionally have values for both $\dot{y}$ and $\dot{z}$.
We can further substitute, which leads us to
\[
\ddot{x}=\dot{y}z+y\dot{z}= -xz^{2}-k^{2}xy^{2}.
\]

### 2016-03-22 resume/education.tex
updated many things

\noindent\textbf{\large Education}
\begin{enumerate}[label={\Roman*}.]
\item \textbf{Christopher Newport University $\cdot$ 2013 - Present}
\begin{itemize}
\item Pursuing a B.S. in Mathematics and a B.S. in Computer Science
\item Serving as Secretary for the Society of Physics club
\item Employed by the Center for Academic Success as a tutor
\item Earned Dean's List every semester
\item Relavent coursework includes
\begin{itemize}
\item UNIX Operating Systems, C++ Programming, Java Programming, Android Programming, Programming Language
Concepts, Data Structures, Algorithms, Computer Hardware and Design, Discreet Mathematics, Linear Algebra,
Calculus I - IV, Real Analysis, Partial and Ordinary Differential Equations, Writing in Mathematics using
\hologo{LaTeX}
\end{itemize}
\item Expected to graduate in May 2017
\end{itemize}
\end{enumerate}

>>>>

\noindent\textbf{\large Education}
\begin{enumerate}[label={\Roman*}.]
\item \textbf{Christopher Newport University $\cdot$ 2013 - Present}\\
Bachelors of Science $-$ Mathematics $\cdot$ Bachelors of Science $-$ Computer Science
\begin{itemize}
\item Community Involvement and Accomplishments
\begin{itemize}
\item Employed by the Center for Academic Success as a tutor in Mathematics and Computer Science
\item Inducted into the Virginia Mu chapter of Pi Mu Epsilon
\item Served as Secretary for the Society of Physics club
\item Earned Dean's List consistently
\end{itemize}
% \newpage
\item Relevant coursework includes
\begin{itemize}
\item Mathematical Education
\begin{quote}
Calculus I - IV, Linear Algebra, Real Analysis, Partial and Ordinary Differential Equations, Writing in
Mathematics using \hologo{LaTeX}, Proofs and Discreet Mathematics, Number Theory, Independent Study in
Partial Differential Equations
\end{quote}
\item Computer Science Education
\begin{quote}
UNIX Operating Systems, C++ Programming, Java Programming, Android Programming, Programming Language
Concepts, Data Structures, Algorithms, Computer Hardware and Design, Discreet Mathematics
\end{quote}
\end{itemize}
\end{itemize}
\end{enumerate}

### 2016-03-22 resume/work.tex
updated many things

\noindent\textbf{\large Work Experience}
\begin{enumerate}[label={\Roman*}.]
\item National Aeronautics and Space Administration $\Bigcdot$ November 2015 - Present
\begin{itemize}
\item Developed Android applications for Google Glass, Vuzix, and Recon Jet headsets
\item Used git extensively for version control
\item Wrote code primarily in Java
\end{itemize}
\item Freelance Application Developer $\Bigcdot$ July 2015 - Present
\begin{itemize}
\item Built a location based audio application called Audionce, written for Android and iOS.
\item Created a quiz web-application called WhensIt for the Public History Center at Christopher Newport
University
\item Built websites using JavaScript, HTML5, CSS3, and PHP
\end{itemize}
\item Christopher Newport University $\Bigcdot$ September 2013 - Present
\begin{itemize}
\item IT Customer Service Representative
\begin{itemize}
\item Aided customers with various software related IT issues
\item Assisted technicians with tasks such as installing hardware
\end{itemize}
\item Tutor for the Center for Academic Success
\begin{itemize}
\item Tutored several subjects including Mathematics, Computer Engineering, and Computer Science
\item Participated in both one on one tutoring and group tutoring
\end{itemize}
\end{itemize}
\item Kirk Family YMCA $\Bigcdot$ August 2009 - August 2015
\begin{itemize}
\item Lead Swim Instructor
\begin{itemize}
\item Managed a team of swim instructors that taught and oversaw various camps and lessons
\item Taught swimming lessons to children and adults of all ages
\item Promoted to manager in May 2015
\end{itemize}
\item Lifeguard
\begin{itemize}
\item Attended trainings for CPR and AED certifications, as well as First Aid and lifesaving skills
\item Worked to create and maintain a safe environment for all patrons of the pool by enforcing rules and
policies of the YMCA
\end{itemize}
\end{itemize}
\end{enumerate}

>>>>

\noindent\textbf{\large Work Experience}
\begin{enumerate}[label={\Roman*}.]

\item MyNewLeaf, LLC $\Bigcdot$ January 2016 - Present
\begin{itemize}
\item Contracted to develop Android version of iOS application
\item Collaborated with a large team of designers, managers, and programmers
\item Served as lead programmer for Android version of application
\end{itemize}

\item National Aeronautics and Space Administration (NASA) $\Bigcdot$ November 2015 - Present
\begin{itemize}
\item Developed Android applications for Google Glass, Vuzix, and Recon Jet headsets
\item Worked closely with a university professor to plan and create the application
\item Participated in laser safety training
\end{itemize}

\item Application Developer $\Bigcdot$ July 2015 - Present
\begin{itemize}
\item Built a location based audio application called Audionce, written for Android and iOS
\item Created a quiz web-application called WhensIt for the Public History Center at Christopher Newport
University
\item Built websites using JavaScript, HTML5, CSS3, and PHP
\end{itemize}

\item Christopher Newport University $\Bigcdot$ September 2013 - Present
\begin{itemize}
\item IT Customer Service Representative
\begin{itemize}
\item Aided customers with various software related IT issues
\item Assisted technicians with tasks such as installing hardware
\end{itemize}
\item Tutor for the Center for Academic Success
\begin{itemize}
\item Tutored several subjects including Mathematics (mostly Calculus), Computer Engineering, and
Computer Science
\item Participated in both one on one tutoring and group tutoring
\item Created various resources for other Calculus tutors to use
\end{itemize}
\end{itemize}

\newpage
\item Kirk Family YMCA $\Bigcdot$ August 2009 - August 2015
\begin{itemize}
\item Lead Swim Instructor
\begin{itemize}
\item Managed a team of swim instructors that taught and oversaw various camps and lessons
\item Taught swimming lessons to children and adults of all ages
\item Promoted to manager in May 2015
\end{itemize}
\item Lifeguard
\begin{itemize}
\item Attended trainings for CPR and AED certifications, as well as First Aid and lifesaving skills
\item Worked to create and maintain a safe environment for all patrons of the pool by enforcing rules and
policies of the YMCA
\end{itemize}
\end{itemize}
\end{enumerate}
